### 2018-06-22 Paper/paper.tex
Updated Draft

\section{Abstract}     
Paths on the Autonomous Systems (AS) graph of the Internet
derived from the Border Gateway Protocol (BGP) can be used by researchers to
understand the dynamics of Internet topology and to interpret how that
topology may enable nations to enact censorship, surveillance, or other
Internet control measures. Unfortunately datasets of these paths are not
generally made publicly available, and paths collected from measurements such as
traceroute measurements or BGP probes tend to be incomplete. Simulation
frameworks have been used to generate AS paths based on empirical AS graphs.
We have reimplemented one such framework, BGPSim \cite{quicksand} in Python as
an efficient, open source BGP path simulation tool called BGPSimPy. With this
tool we produced publicly available routing tree datasets that will enable
future research on AS level topology. Previous research endeavors in this
direction have only identified chokepoints in single snapshots. We apply the
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years in order to introduce a new technique to investigate the
evolution of the complex and dynamic AS level Internet topology. As an
application of the routing trees we compare multiple qualitative sources of
Internet freedom and censorship with chokepoint metrics in order to interpret
the relationship between AS level topology and actual censorship activity.

@@

paths {\color{blue}cite?}. It is also important that paths from all ASes be utilized to
get a complete picture of Internet topology. One technique for generating such

@@

admins.     

@@

\section{BGPSimPy}
In order to conduct an analysis on AS level topology, the paths
generated by the Border Gateway Protocol (BGP) have to be modeled. A
traditional approach is to use a tool like traceroute to collect paths via
measurement, or at a larger scale use a selection of BGP data collectors with
a tool like BGPStream \cite{bgpstream} \cite{traceroute}. Unfortunately, these
techniques require extensive collection time and are still susceptible to
errors and incomplete data. There is no readily available BGP path dataset
with which to study. Thus, researchers must turn to simulation to find
accurate BGP paths.     
\par One such simulation framework, the previously
mentioned BGPSim, was developed by Gill et al. \cite{quicksand} as a tool for
quickly estimating AS paths from an input AS graph. This AS graph could be
taken from a set of inferred AS relationships, such as the CAIDA AS
relationship dataset \cite{CAIDA}. BGPSim outputs routing trees, which contain
all paths from leaf ASes to the root AS, for each AS in the AS graph. The
routes are selected using a modified breadth-first search that selects with
the following priorities: shortest path, local preference (using the rules
from Gao \cite{Gao}), and finally tie break of all equally good paths. With
these priorities, BGPSim generates a realistic collection of AS level paths,
which are ideal for use in Internet topology studies.
\par 
Unfortunately, BGPSim is not ready to deploy immediately and easily, as would be necessary
for a tool dedicated to allow fast monitoring of the Internet's overall state.
This is largely due to the fact that BGPSim is written in C\# (affecting its
ability to be used in a cross-platform way) with DryadLinq (a deprecated C\#
library) for distributed computing. As a remedy to these problems, we have
reimplemented BGPSim under the name BGPSimPy. BGPSimPy is written purely in
python, making it cross platform and easy to integrate. Additionally,
distributed computing is now achieved with MPI using mpi4py, a framework that
is supported on many computer clusters.

@@

\section{Applications of Routing Trees}
\subsection{Measuring Chokepoints in AS-level Paths}
Once we generated routing trees, we
could use the paths to identify chokepoints, or ASes that intercept large
portions of paths, on the AS graph. Specifically, we chose to evaluate border
ASes, or ASes that could reach an AS registered to a different nation with one
hop. By selecting border ASes we could locate the ASes that intercepted
traffic into a nation (via out-to-in paths), as in a foreign attempt to access
a domestic website, or ASes that intercepted traffic out of a nation, as in a
domestic attempt to access a foreign website (via in-to-out paths). We choose
to make a distinction between these two path types to better understand the
implications of the chokepoints belonging to each nation.
\par To evaluate border ASes we use the metric of chokepont potential, defined here to be the
ratio of the number of paths intercepted by a border AS to the number of paths
for that nation, as shown in equation \ref{eqn:chokePointPotential}. This
metric is calculated separately for both in-to-out paths and out-to-in paths.
This calculation is performed by traversing the routing trees and keeping
record of which border nodes intercept each path, as well as what path type is
currently being traversed with regards to the host nation of the border AS in
question. Once all paths are traversed, the totals are compiled together, with
a chokepoint potential value stored for each border AS.
\par 
The chokepoint potentials of the border ASes allowed us to investigate the state of the AS-
level topology of the Internet for any given set of initial AS relationships.
We first looked at how many ASes each nation is required to control to
intercept a percentage of paths. For this test, we chose 90\%, as this would
indicate a clear control of Internet paths for the given country and was also
the percentage used in \cite{throats}. Additionally, we determined this value
for each nation for multiple timestamps, yielding our initial picture of the
evolution of Internet topology. The results of this test for some nations of
interest are shown in figure \ref{fig:NumToIntercept}.

@@

\par 
The variation between the different nations highlights the importance of measuring
chokepoints on the national level. Trends exist within a nation, but nations
tend to have surprisingly unique AS graph dynamics. China shows a striking
increase in chokepoint potential. In order to control 90% of paths, China has
to utilize a strikingly few number of ASes. This suggests an ever
strengthening backbone in the Chinese Internet. Conversely, the trend that
Brazil's capability to intercept paths is decreasing is also evident in these
results. This could be the effect of an expansion of infrastructure, leading
to more border ASes and more diverse paths in and out of the country. {\color{blue}Maybe
there is a source to support this?} Another interesting element of these
results is the dynamic behavior for some nations. It seems that in some cases,
when it becomes easier to control many paths, it becomes more difficult to
control all paths. {\color{blue}Not sure of implications, needs work here}

\subsection{Comparing Internet Topology with Freedom On The Net}
While research in the past \cite{throats} has connected AS-level chokepoints with the capability of
a nation to conduct censorship, linking the topology based measurements to
other attempts at measuring Internet freedom has not been done before to the
best of our knowledge. Such a connection would bridge the gap between a
dynamic system driven by many factors, both automatic and instituted, and
qualitative classification of nations.
\par Freedom House's Freedom On The Net
(FOTN) report \cite{FOTN}, is an annual ranking and analysis of Internet
freedom, interpreted from multiple measures including obstacles to access,
limits on content, and violations of user rights. The FOTN includes a ranking
of nations by a freedom index, where a higher number indicates a less free
Internet for that nation. The index is calculated from a series of questions
that are evaluated according to various sources regarding each nation. These
questions encompass multiple categories, including government filtering and
censorship of web traffic. In order to investigate whether the topology of a
nations ASes is related to Internet freedom, we compare the FOTN freedom index
with the ease with which a nation can control AS level paths. In figure
\ref{fig:fotn} we plot the number of ASes required for a nation to control 90%
of paths with that nation's freedom index for multiple timestamps of AS
relationships.

@@

\end{document}

>>>>

\section{Abstract}     
Paths on the Autonomous Systems (AS) graph of the Internet
derived from the Border Gateway Protocol (BGP) can be used by researchers to
understand the dynamics of Internet topology and to interpret how that
topology may enable nations to enact censorship, surveillance, or other
Internet control measures. Unfortunately datasets of these paths are not
generally made publicly available, and paths collected from measurements such as
traceroute or BGP probes tend to be incomplete. Simulation
frameworks have been used to generate AS paths based on empirical AS graphs.
We have reimplemented and extended one such framework, BGPSim \cite{quicksand} in Python as
an efficient, open source BGP path simulation tool called BGPSimPy. With this
tool we produced publicly available routing tree datasets that will enable
future research on AS level topology. We introduce a metric, \textit{chokepoint potential},
in order to use routing trees to interpret the capability for border ASes (those one hop away from
an AS in a different nation) to enact censorship or surveillance. With the entire set of
routing trees we demonstrate that we can expose the choke points of AS-level routing for
any nation. Previous research endeavors in this
direction have only identified chokepoints in single snapshots. We apply the
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years in order to introduce a new technique to investigate the
evolution of the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible. As an
application of the routing trees we compare multiple qualitative sources of
Internet freedom and censorship with chokepoint metrics in order to interpret
the relationship between AS level topology and actual censorship activity, providing
illustration of new ways to monitor which governments can easily control the flow of 
information in their nations.

@@

paths {\color{blue}cite?}. 
In light of these issues, BGP researchers often employ more abstract models of BGP.
For instance, the authors in \cite{converge} developed a simplification of BGP in order
to estimate important convergence properties. In order to evaluate Internet chokepoints,
an accurate set of paths between all AS pairs must generated. One technique for generating such

@@

administrators.     

@@

We are not the first to investigate the relationship between Internet freedom and
AS-level topology. Similar techniques have been used to classify nations according
to the connectivity of their ASes \cite{politicsrouting}. This has only been done for a
single moment in time, however, making the results limited in terms of stability and predictability.
Additionaly, previous work has not used country level chokepoints as the link between Internet topology
and censorship or surveillance practices. The work in \cite{politicsrouting} chose to relate Internet topology
to the Freedom of the Press measure from freedom house instead of the Freedom On The Net score. They chose to do this
to include more nations. Additionally, they didn't include the United States and Russia in their experiments because they were
outliers in regards to their topologies. Through our approach we hope to extend this previous work by finding an interesting metric for
understanding the dynamics of all nations, as well as targeting our results more specifically to Internet freedom by using the Freedom On
The Net score as our metric for Internet freedom. Through our techniques, we provide a simple metric that not only 
sheds light on the relationship between topology and Internet freedom, but reveals currently free
nations that could easily implement censorship if their governments decided to.

\section{BGPSimPy}
In order to conduct an analysis on AS level topology, the paths
generated by the Border Gateway Protocol (BGP) have to be modeled. A
traditional approach is to use a tool like traceroute to collect paths via
measurement, or at a larger scale use a selection of BGP data collectors with
a tool like BGPStream \cite{bgpstream} \cite{traceroute}. Unfortunately, these
techniques require extensive collection time and are still susceptible to
errors and incomplete data. There is no readily available BGP path dataset
with which to study. Thus, researchers must turn to simulation to find
accurate BGP paths.     
\par One such simulation framework, the previously
mentioned BGPSim, was developed by Gill et al. \cite{quicksand} as a tool for
quickly estimating AS paths from an input AS graph. This AS graph could be
taken from a set of inferred AS relationships, such as the CAIDA AS
relationship dataset \cite{CAIDA}. BGPSim outputs routing trees, which contain
all paths from leaf ASes to the root AS, for each AS in the AS graph. The
routes are selected using a modified breadth-first search that selects with
the following priorities: shortest path, local preference (using the rules
from Gao \cite{gao}), and finally tie break of all equally good paths. With
these priorities, BGPSim generates a realistic collection of AS level paths,
which are ideal for use in Internet topology studies.
\par 
Unfortunately, BGPSim is not ready to deploy immediately and easily, as would be necessary
for a tool dedicated to allow fast monitoring of the Internet's overall state.
This is largely due to the fact that BGPSim is written in C\# (affecting its
ability to be used in a cross-platform way) with DryadLinq (a deprecated C\#
library) for distributed computing. As a remedy to these problems, we have
reimplemented BGPSim under the name BGPSimPy. BGPSimPy is written purely in
python, making it cross platform and easy to integrate. Additionally,
distributed computing is now achieved with MPI using mpi4py, a framework that
is supported on many computer clusters.

@@

\section{Applications of Routing Trees}
\subsection{Measuring Chokepoints in AS-level Paths}

It is well documented that the AS graph is composed of a hierarchy of ASes, such that the ASes
distributed in tiers. This tier list includes a very small set of tier-1 ASes
that are able to provide the highest levels of connectivity to the rest of the Internet \cite{hierarchy}.
This hierarchy is generally viewed in a way agnostic to national boundaries. It is
possible, however, that more ASes exhibit potential to control information flow in the sense that
chokepoints can exist at the national level. While these chokepoints might not provide extensive connectivity
to the entire set of ASes, they may provide similar connectivity to the interior ASes of a particular nation. 
Thus, a technique to conduct a fine-grained analysis of the number of paths intercepted by ASes that provide access
in and out of nations is a worthwhile pursuit. Previous works have also not provided an analysis of the development of
the AS hierarchy over time. The monitoring of national chokepoints over time is relevant to predicting the stability of the
future Internet, identifying key censorship bottlenecks, and understanding the potential for national governments to conduct
surveillance on foreign traffic.

Once we generated routing trees using BGPSimPy, we
used the paths to identify national chokepoints. Specifically, we chose to evaluate border
ASes, or ASes that could reach an AS registered to a different nation with one
hop. By selecting border ASes we could locate the ASes that intercepted
traffic into a nation (via out-to-in paths), as in a foreign attempt to access
a domestic website, or ASes that intercepted traffic out of a nation, as in a
domestic attempt to access a foreign website (via in-to-out paths). We choose
to make a distinction between these two path types to better understand the
implications of the chokepoints belonging to each nation.

\par To evaluate border ASes we use the metric of chokepont potential, defined here to be the
ratio of the number of paths intercepted by a border AS to the number of total path interceptions
possible for that nation. If $P_c$ is the set of all paths (either in-to-out or out-to-in) belonging to nation $c$ and 
$B_p$ is the set of all border nodes within a path $p$, the chokepoint potential for a border node $b$ is defined in equation \ref{eqn:chokePointPotential}
This metric is calculated separately for both in-to-out paths and out-to-in paths.
This calculation is performed by traversing the routing trees and keeping
record of which border nodes intercept each path, as well as what path type is
currently being traversed with regards to the host nation of the border AS in
question. Once all paths are traversed, the totals are compiled together, with
a chokepoint potential value stored for each border AS.

\begin{equation}\label{eqn:chokePointPotential}
CP_b = \frac{|\{p \in P_c \textrm{ s.t. } \{b\} \subseteq B_p\}|}{\sum_{p \in P_c}|B_p|}
\end{equation}

\par 
The chokepoint potentials of the border ASes allowed us to investigate the state of the AS-
level topology of the Internet for any given set of initial AS relationships.
We first looked at how many ASes each nation is required to control to
intercept a percentage of paths. For this test, we chose 90\%, as this would
indicate a clear control of Internet paths for the given country and was also
the percentage used in past studies \cite{throats}. Additionally, we determined this value
for each nation for multiple timestamps, yielding our initial picture of the
evolution of Internet topology. The results of this test for some nations of
interest are shown in figure \ref{fig:NumToIntercept}.

@@

\par 
The variation between the different nations highlights the importance of measuring
chokepoints on the national level. Trends exist within a nation, but nations
tend to have surprisingly unique AS graph dynamics. China shows a striking
increase in chokepoint potential. In order to control 90\% of paths, China has
to utilize a strikingly few number of ASes. This suggests an ever
strengthening backbone in the Chinese Internet. Conversely, the trend that
Brazil's capability to intercept paths is decreasing is also evident in these
results. This could be the effect of an expansion of infrastructure, leading
to more border ASes and more diverse paths in and out of the country. {\color{blue}Maybe
there is a source to support this?} Another interesting element of these
results is the dynamic behavior for some nations. It seems that in some cases,
when it becomes easier to control many paths, it becomes more difficult to
control all paths. {\color{blue}Not sure of implications, needs work here}

\subsection{Comparing Internet Topology with Freedom On The Net}
While research in the past has connected AS-level topology with Internet freedom 
and censorship \cite{throats}\cite{politicsrouting}, the evolution of this relationship has
not been investigated across multiple years. We also provide the first attempt to connect the
metric of chokepoint potential with the Internet freedom of nations, creating insight into the
connection between the state of Internet topology and efforts to limit Internet freedoms.
\par Freedom House's Freedom On The Net
(FOTN) report \cite{FOTN}, is an annual ranking and analysis of Internet
freedom, interpreted from multiple measures including obstacles to access,
limits on content, and violations of user rights. The FOTN includes a ranking
of nations by a freedom index, where a higher number indicates a less free
Internet for that nation. The index is calculated from a series of questions
that are evaluated according to various sources regarding each nation. These
questions encompass multiple categories, including government filtering and
censorship of web traffic. In order to investigate whether the topology of a
nations ASes is related to Internet freedom, we compare the FOTN freedom index
with the ease with which a nation can control AS level paths. In figure
\ref{fig:fotn} we plot the number of ASes required for a nation to control 90%
of paths with that nation's freedom index for multiple timestamps of AS
relationships.

@@

\end{document}\grid
